AttCRISPR : an spacetime interpretable model for sgRNA efficiency prediction

### 2020-10-19 Paper/main.tex
10-19 paper

Text
\begin{table}[!tpb]
    \processtable{wait2write\label{Tab:02}} 
    {\begin{tabular}{@{}llll@{}}\toprule
        Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
        XGBoost & 0.845 & 0.831 & 0.818\\
        MLP & 0.842 & 0.846 & 0.844\\
        CNN & 0.846 & 0.831 & 0.834\\
        RNN & 0.856 & 0.849 & 0.851\\
        TAC & 0.857 & 0.844 & 0.851\\
        SpAC & 0.862 & 0.854 & 0.857\\
        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
\end{table}

@@

>>>>

In Table~\ref{Tab:02}, we list the performance of methods in spatial or temporal domain and the stacking of methods. 
Temporal AttCRISPR, TAC for short, achieved Spearman correlation coefficients of 0.857, 0.844, 0.851 in above three dataset. 
Spatial AttCRISPR, SpAC for short, corresponds to 0.862, 0.854, 0.857. In the absence of hand-crafted biological features. 
Ensemble AttCRISPR achieve the best performance of our knowledge, corresponds to 0.868, 0.859, 0.862. 
\begin{table}[!tpb]
    \processtable{wait2write\label{Tab:02}} 
    {\begin{tabular}{@{}llll@{}}\toprule
        Method & WT-SpCas9 & eSpCas9(1.1) & SpCas9-HF1\\\midrule
        XGBoost & 0.845 & 0.831 & 0.818\\
        MLP & 0.842 & 0.846 & 0.844\\
        CNN & 0.846 & 0.831 & 0.834\\
        RNN & 0.856 & 0.849 & 0.851\\
        TAC & 0.857 & 0.844 & 0.851\\
        SpAC & 0.862 & 0.854 & 0.857\\
        \textbf{EnAC} & \textbf{0.868} & \textbf{0.859} & \textbf{0.862}\\
        CRISPRpred(SEQ) & 0.838 & 0.830 & 0.821\\
        \botrule
    \end{tabular}}\footnotesize\setlength{\parindent}{2em}{\emph{Note}: wait2write}
\end{table}

@@

text
